### 2012-03-27 exam4/2.tex
fix compilation problems in soln

\item Design the {\tt height} method, which computes the height of the
  tree (i.e., the maximum distance from the root to a leaf).  The
  example tree has a height of 4.

@@

interface TwoTree extends Tree {}
interface ThreeTree extends Tree {}
\end{verbatim}
\newpage
\begin{verbatim}
//> 4pts for class definitions
//> 3pts for method definitions
class Leaf implements TwoTree, ThreeTree {
  String val;

@@

class TwoNode implements TwoTree {
  ThreeTree left;
  ThreeTree right;

  Integer height() { return max(this.left.height(), this.right.height()); }
}

@@

  Integer height() { return max(this.left.height(),
                                this.mid.height(),
                                this.right.height()); }
}

Tree r = new Leaf("Rhinocerous");
Tree h = new Leaf("Hat");
Tree b = new Leaf("Bread");
Tree t1 = new ThreeNode(new Leaf("Zebra"),new Leaf("Dog"),new Leaf("Cat"));
Tree t2 = new TwoNode(t1,r);
Tree t3 = new ThreeNode(b,h,t2);

//> 3pts for tests
t3.height() -> 4
r.height() -> 1
t2.height() -> 3
\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

\begin{solution}
\begin{verbatim}
//> 2pts parameterization
//> 2pts methods
interface TreeVisitor<T> {
  T visitLeaf(String s);
  T visitTwoNode(ThreeTree l, ThreeTree r);
  T visitThreeNode(TwoTree l, TwoTree r);
}

@@

\begin{solution}
\begin{verbatim}
//> 2pts class def
//> 2pts implementations
class CountVisitor implements TreeVisitor<Integer> {
  Integer visitLeaf(String s) { return 1; }
  Integer visitTwoNode(Tree l, Tree r) { return l.visit(this) + r.visit(this); }
  Integer visitThreeNode(Tree l, Tree m, Tree r) { 
     return l.visit(this) + r.visit(this) + m.visit(this);
  }
}
//> 2pts tests
r.visit(new CountVisitor()) -> 1
t2.visit(new CountVisitor()) -> 4
t3.visit(new CountVisitor()) -> 6
\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}
// 2pts class def
// 3pts methods
class LongestVisitor implements TreeVisitor<String> {
  String visitLeaf(String s) { return s; }
  String visitTwoNode(Tree l, Tree r) { 
     String s1 = l.visit(this);
     String s2 = r.visit(this);
     return (s1.length() > s2.length())?s1:s2;
  }
  String visitThreeNode(Tree l, Tree m, Tree r) { 
     String s1 = l.visit(this);
     String s2 = r.visit(this);
     String s3 = m.visit(this);
     if (s1.length() > s2.length() && s1.length() > s3.length())
       return s1;
     else if (s2.length() > s3.length())
       return s2;
     else
       returns s3;
  }
}
//> 2pts tests
h.visit(new LongestVisitor()) -> "Hat"
t2.visit(new LongestVisitor()) -> "Rhinocerous"
t3.visit(new LongestVisitor()) -> "Rhinocerous"
\end{verbatim}
\end{solution}

>>>>

\item Design the {\tt height} method, which computes the height of the
  tree (i.e., the maximum distance from the root to a leaf).  The
  example tree has a height of 4. You may find the function
  \verb|Math.max| useful; it takes two numbers and produces the
  largest.

@@

interface TwoTree extends Tree {}
interface ThreeTree extends Tree {}
\end{verbatim}
\newpage
\begin{verbatim}
//> 4pts for class definitions
//> 3pts for method definitions
class Leaf implements TwoTree, ThreeTree {
  String val;
  Leaf(String v) { val = v; }

@@

class TwoNode implements TwoTree {
  ThreeTree left;
  ThreeTree right;
  TwoNode(ThreeTree l, ThreeTree r) { left = l; right = r; }

  Integer height() { return Math.max(this.left.height(), this.right.height()); }
}

@@

  TwoNode(ThreeTree l, ThreeTree r) { left = l; right = r; }

  Integer height() { return Math.max(this.left.height(),
                                     Math.max(this.mid.height(),
                                              this.right.height())); }
}
ThreeTree r = new Leaf("Rhinocerous");
TwoTree h = new Leaf("Hat");
TwoTree b = new Leaf("Bread");
ThreeTree t1 = new ThreeNode(new Leaf("Zebra"),new Leaf("Dog"),new Leaf("Cat"));
TwoTree t2 = new TwoNode(t1,r);
Tree t3 = new ThreeNode(b,h,t2);
//> 3pts for tests
t3.height() -> 4
r.height() -> 1
t2.height() -> 3
\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

\begin{solution}
\begin{verbatim}
//> 2pts parameterization
//> 2pts methods
interface TreeVisitor<T> {
  T visitLeaf(String s);
  T visitTwoNode(ThreeTree l, ThreeTree r);
  T visitThreeNode(TwoTree l, TwoTree m, TwoTree r);
}

@@

\begin{solution}
\begin{verbatim}
//> 2pts class def
//> 2pts implementations
class CountVisitor implements TreeVisitor<Integer> {
  Integer visitLeaf(String s) { return 1; }
  Integer visitTwoNode(ThreeTree l, ThreeTree r) { return l.visit(this) + r.visit(this); }
  Integer visitThreeNode(TwoTree l, TwoTree m, TwoTree r) { 
     return l.visit(this) + r.visit(this) + m.visit(this);
  }
}
//> 2pts tests
r.visit(new CountVisitor()) -> 1
t2.visit(new CountVisitor()) -> 4
t3.visit(new CountVisitor()) -> 6
\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}
// 2pts class def
// 3pts methods
class LongestVisitor implements TreeVisitor<String> {
  String visitLeaf(String s) { return s; }
  String visitTwoNode(ThreeTree l, ThreeTree r) { 
     String s1 = l.visit(this);
     String s2 = r.visit(this);
     return (s1.length() > s2.length())?s1:s2;
  }
  String visitThreeNode(TwoTree l, TwoTree m, TwoTree r) { 
     String s1 = l.visit(this);
     String s2 = r.visit(this);
     String s3 = m.visit(this);
     if (s1.length() > s2.length() && s1.length() > s3.length())
       return s1;
     else if (s2.length() > s3.length())
       return s2;
     else
       return s3;
  }
}
//> 2pts tests
h.visit(new LongestVisitor()) -> "Hat"
t2.visit(new LongestVisitor()) -> "Rhinocerous"
t3.visit(new LongestVisitor()) -> "Rhinocerous"
\end{verbatim}
\end{solution}
